Verifying Demonstrations

### 2018-11-15 paper/intro.tex
Fixes typos and cleans up title code

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{related-work}).
However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times ---, which in turn increases the error of the estimation.
In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claims should be verifiable).
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to magically prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity and that any witnessing is also unlinkable.
%Seb: in the sentence above I am not sure that the word unlinkable will be necessary clear

@@

%In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.

>>>>

Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{related-work}).
However, most of them lack precision (\ie they have large error margins) and 
they can only give an estimate for a particular snapshot in time (\eg at the 
peak of the event). In particular, the existing methods cannot reliably 
estimate the cumulative participation count --- at least not without counting 
some persons multiple times --- which in turn increases the error of the 
estimation.
In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice 
and Grace from cheating by providing verifiable claims.
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to magically prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity and that any witnessing is also unlinkable.
\seb{in the sentence above I am not sure that the word unlinkable will be 
  necessary clear}

@@

%In this paper, our first main contribution is to propose \CROCUS, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
